---
title: "Report"
author: "Linh, Yolanda"
date: "10/1/2020"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(lubridate)
library(rpart)
library(rpart.plot)
library(vcd)
```

## Load Data

Loading data from server. Data should be from Dec 19, 2019. Showing first few data in the dataset:

```{r load_data, echo=FALSE, message=FALSE}
#Pull data from server and select data since Dec 19, 2019
data <- read_csv("https://www.stat2games.sites.grinnell.edu/data/epidemic/getdata.php")
```

```{r data_cleaning, echo=FALSE}
#Filter by date benchmark
data <- data %>% filter(Level > 0)
benchmark <- as.Date("2019-12-19")
data = data %>% filter(Date > benchmark)

#Converting PlayerID and GroupID to lower case
data$PlayerID <- tolower(data$PlayerID)
data$GroupID <- tolower(data$GroupID)

#Convering Certain Columns to Factors
data$TurretType <- as.factor(data$TurretType)
data$Level <- as.factor(data$Level)
data$Upgrade <- as.factor(data$Upgrade)
data$Medicine <- as.factor(data$Medicine)
data$Virus <- as.factor(data$Virus)
data$Wave <- as.factor(data$Wave)
data$Location <- as.factor(data$Location)

#Creating Additional Columns
data = mutate(data, Killed = 1)

#Tidy data
destroyed = data[rep(row.names(data), data$Destroyed), ]
missed = data[rep(row.names(data), data$Shot - data$Destroyed), ]
missed$Killed = 0
data = rbind(destroyed, missed)

#Drop unneccesary columns
data = select(data, -c("Shot", "Destroyed"))
data = rename(data, Destroyed = Killed)

#Show data
knitr::kable(data[1:5, ])
```

## Probabilities

```{r split_by_level, echo=FALSE}
#Splitting data by level
level1 <- data %>% filter(Level == "1")
level2 <- data %>% filter(Level == "2")
level2B <- data %>% filter(Level == "2B")
level3 <- data %>% filter(Level == "3")
```

```{r define_funtion, echo=FALSE}
# Set attributes for tree model
method = "anova" #regression tree
control = rpart.control(cp = -1) #build a fully grown tree

# Function to draw tree out from built model
draw_tree = function(model, tree_name){
  rpart.plot(model, main=tree_name, type = 5, extra = 0, branch = .2)
  rpart.rules(model)
}

#Function to draw mosaic graph from data by level
draw_mosaic = function(table, graph_name){
  mosaic(table, shade = TRUE, main = graph_name)
}
```

### Level 1

Explanatory variables: Medicine, Virus

#### Decision Tree

```{r level1_tree, echo=FALSE, warning=FALSE}
model_level1 = rpart(Destroyed ~ Medicine + Virus, method = method, data = level1, control = control)
draw_tree(model_level1, "Level 1")
```

#### Mosaic

```{r level1_mosaic, echo=FALSE, warning=FALSE}
table1 <- xtabs(Destroyed ~ Medicine + Virus, level1)
draw_mosaic(table1, "Level 1")
```

### Level 2

Explanatory variables: Medicine

#### Decision Tree

```{r level2_tree, echo=FALSE, warning=FALSE}
model_level2 = rpart(Destroyed ~ Medicine, method = method, data = level2, control = control)
draw_tree(model_level2, "Level 2")
```

#### Mosaic

```{r level2_mosaic, echo=FALSE, warning=FALSE}
table2 <- xtabs(Destroyed ~ Medicine, level2)
draw_mosaic(table2, "Level 2")
```

### Level 2B (Advanced Mode)

Explanatory variables: TurretType, Medicine

#### Decision Tree

```{r level2B_tree, echo=FALSE, warning=FALSE}
model_level2B = rpart(Destroyed ~ TurretType + Medicine, method = method, data = level2B, control = control)
draw_tree(model_level2B, "Level 2B")
```

#### Mosaic

```{r level2B_mosaic, echo=FALSE, warning=FALSE}
table2B <- xtabs(Destroyed ~ TurretType + Medicine, level2B)
draw_mosaic(table2B, "Level 2B")
```

### Level 3

Explanatory variables: Medicine, Virus

#### Decision Tree

```{r level3_tree, echo=FALSE, warning=FALSE}
model_level3 = rpart(Destroyed ~ Medicine + Virus, method = method, data = level3, control = control)
draw_tree(model_level3, "Level 3")
```

#### Mosaic

```{r level3_mosaic, echo=FALSE, warning=FALSE}
table3 <- xtabs(Destroyed ~ Medicine + Virus, level3)
draw_mosaic(table3, "Level 3")
```